
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{thanos-cv} 

\begin{document}

\header{Athanasios}{Chatzoglou}{} 

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside}
~
~
~
~
~
~
~
~
~
~
\section{{\color{gray}{\FA \faHome}}contact}
Amanuensvägen 3/1004
11416 Solna
Stockholm
Sweden
~
{\color{orange}{\FA \faUser}}{ Sv Pn: 870831-1512}
~
{\color{green!150}{\FA \faPhone}}{ +46 (0) 76 715 90 10}
{\color{gray}{\FA \faEnvelope}} \href{mailto:chatzoglou87@gmail.com}{chatzoglou87@gmail.com}
{\color{linkedin}{\FA \faLinkedin}} \href{http://lnkd.in/buQYKsf}{LinkedIn}
~

\section{technical}
Linux, Office suites
UML, Java
HTML/CSS, Git
\LaTeX, SPSS
Requisite Pro, WEKA
SEO, Redmine
Technical writing
~

\section{languages}
Greek -- native
English -- fluent
Swedish -- intermediate
\end{aside}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2012--2014}
{M.Sc. {\normalfont in Strategic IT Management}}
{Stockholm University, Sweden}
{\emph{Focus on business \& IT alignment, requirements engineering, data mining and business intelligence.\\
Master thesis on risk analysis and project management.}}\\
%------------------------------------------------
\entry
{2006--2011}
{B.B.A. {\normalfont Bachelor of Business Administration}}
{University of Macedonia, Greece}
{Four year curriculum focused on financial economics, business analysis, management, marketing and accounting.}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--20/09}
{Skanatek AB}
{Sweden}
{\emph{Business Development Intern at a young Swedish startup (6 months)} 
\begin{itemize}[leftmargin=*]
\item In charge of the composition of the company's business plan.
\item Intimately involved in the development and shape of the company's final main product.
\item Responsible for the creation and execution of customer development tasks.
\item Intimately involved in the writing up of all marketing literature.
\item Financial forecasting for various projects pursued by the company, including start-up projects.
\item Market Research and information gathering based on business requirements.
\end{itemize}
}
%------------------------------------------------
\entry
{2010--2011}
{Hellenic Army}
{Greece}
{\emph{Database Administrator} \\
Responsible for the monitoring and administration of databases in the research and informatics office.\\
}
%------------------------------------------------
\entry
{2009--2009}
{Hellenic Fertilizers and Chemicals (ELFE)}
{Greece}
{\emph{Administrative Assistant (summer job)} \\
Administration support in the payroll section.\\
IT support helpdesk.
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------


\section{references}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{John Smith{}}
{Awesome Company AB}
{Founder, Managing Director \& Software Engineer\\
+46 (0) 00 000 00 00\\
\href{mailto:info@awesomecompany.se}{info@awesomecompany.se}\\
}
%------------------------------------------------
\entry
{}
{Bill Gates{}}
{Microsoft}
{CEO\\
+46 (0) 11 111 11 11\\
\href{mailto:bgates@hotmail.com}{bgates@hotmail.com}
}
%----------------------------------------------------------------------------------------
\end{entrylist}
\end{document}